\documentclass[a4,10pt]{article}
%Typeset: LuaLateX
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=0.75cm, top=0.75cm, bottom=0.4cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf, %SourceSansPro-Bold.otf
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}
\setsansfont{SourceSansPro-Semibold.otf}

%%%% Set Page
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color
\definecolor{UI_blue}{RGB}{32, 64, 151}


%%%% Set Sections formatting
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-10pt} \hrulefill \vspace{-6pt}]

%%%% Set Subtext Formatting
\newcommand{\subtext}[1]{
#1\par\vspace{-0.2cm}}

% \newcommand{\subtextit}[1]{\vspace{0.15cm}
% \textit{ #1 \vspace{-0.2cm}} }

%%%% Set Item Spacing
\setlist[itemize]{align=parleft,left=0pt..1em}

%%%% New Itemize "Zitemize" Formatting - tighter spacing than itemize
\newenvironment{zitemize}{
\begin{itemize}\itemsep0pt \parskip0pt \parsep1pt}
{\end{itemize}\vspace{-0.5cm}}


%%%% Define Skills Bold Formatting
\newcommand{\hskills}[1]{
\textbf{\bfseries #1} }

%%%% Set Subsection formatting
\titleformat{\subsection}{\vspace{-0.1cm} 
\bfseries \fontsize{11pt}{2cm}}{}{0em}{}[\vspace{-0.2cm}]

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------

\begin{document}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.29\textwidth}
            (408)-887-0340 \\
            \href{mailto:xavier@loeraflores.tech}{xavier@loeraflores.tech} 
    \end{minipage}% 
    \begin{minipage}[b]{0.4\textwidth}
            \centering
            {\Large Xavier Alejandro Loera Flores} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{Software Engineer}} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.29\textwidth}
            \flushright  %Willing to Relocate
            {\href{https://github.com/xavierloeraflores}{github.com/xavierloeraflores} } \\
            {\href{https://www.linkedin.com/in/xavierloeraflores}{linkedin.com/in/xavierloeraflores} } \\
            {\href{https://loeraflores.com}{Portfolio: https://loeraflores.com}}
    \end{minipage}   
    
\vspace{-0.15cm} 
{\color{UI_blue} \hrulefill}
\end{center}
\vspace{-0.25cm}

{Dedicated and skilled software engineer with 3 years of hands-on experience in developing robust and scalable applications within the Node.js/Next.js ecosystem. Seeking a challenging and impactful role where I can grow and contribute to the success of a dynamic team.}
\vspace{-0.4cm}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SKILLS
%%%%%%% --------------------------------------------------------------------------------------
\section{Skills}
\hskills{Languages}: {Go/Golang, TypeScript, Python, JavaScript,  Java, Swift, SQL (PostgreSQL, MySQL)}  \\
\hskills{Backend}: {Fiber, Node, Express, Flask, FastAPI, Cloud Computing, REST, gRPC, CORS, JWT, NumPy, Pandas, ORM(Drizzle, Prisma) }  \\
\hskills{Frontend}: {React, Next, Svelte, SvelteKit, TailwindCSS, HUGO, HTML, CSS} \\
\hskills{Tools}: {Git, Docker, AWS (EC2, S3), GitHub Actions, Vercel, Railway, Netlify, Insomnia, Postman} \\
\hskills{AI/ML}: {Natural Language Processing, SciKit-Learn, NLTK, Predictive Modeling, Model Persistence \& Deployment, OpenAI API(Chat, Text)}\\
\vspace{-0.2cm}






%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  PROJECTS
%%%%%%% --------------------------------------------------------------------------------------

\section{Projects} 
\subsection*{Scam Scanner: Machine Learning Scam \& Fraud Call Detection System, {\normalsize \normalfont \href{https://github.com/ScamScanners/ScamScanner}{GitHub}} | \normalsize \normalfont \href{https://scam-scanner.vercel.app/}{Live} | \normalsize \normalfont \href{https://devpost.com/software/scamscammer}{DevPost} \hfill}
\begin{zitemize}
       \item {Engineered an end-to-end scalable AI powered multimodal real time detection system by integrating LLMs \& eLLMs using Flask \& Next.js.} \\
        \item {Awarded Groq's "Star Award" by leveraging Groq's chat based LLM to summarize \& analyze call transcripts for key insights.} \\
        \item {Awarded Hume AI's "Most Socially Impactful Empathic AI Integration" by leveraging Hume's Empathetic Voice Interface, Expression Measurement API, \& Custom Models API to develop an empathetic AI system trained on voicemails to detect scam calls in real time.} \\

     \end{zitemize}

%%%%%%% ------------------------------------------------------------------------------- %%%%%%%
\subsection*{Machine Learning Content Moderation System, {\normalsize \normalfont \href{https://github.com/xavierloeraflores/wgu-capstone}{GitHub}} | \normalsize \normalfont \href{https://wgu-capstone-xavier-loera-flores.vercel.app/}{Live} \hfill} 
\begin{zitemize}
       \item {Preprocessed over 50 thousand Tweets for training using Natural Language Processing (NLP) techniques using Pandas \& NLTK.} \\
       \item {Developed, trained, \& persisted 3 linear regression machine learning models using Scikit-Learn that classify offensive text. } \\
       \item {Engineered an end-to-end text based social media feed similar to Twitter using FastAPI, Next.js, \& PostgreSQL.} \\
        \item {Integrated the machine learning model into the posting system to automatically classify and moderate user generated content.} \\
       
     \end{zitemize}



%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  WORK EXPERIENCE
%%%%%%% --------------------------------------------------------------------------------------
\section{Experience}


%%%%%%% ------------------------------------------------------------------------------- %%%%%%%
\subsection*{Fullstack Developer \& Amazon Software Engineering Mentor II {\normalsize \normalfont} \hfill  Feb 2023 --- Present }
\subtext{Fullstack Academy \hfill Remote }
    \begin{zitemize}
        \item Mentored over 100 Amazon software engineers every 6 months and provided guidance, assistance, \& reviews for over 100 weekly projects using technologies such as HTML, CSS, JavaScript, React, Node, Express, PostgreSQL, MongoDB, Netlify, AWS, \& Git.
        \item Developed several apps \& services using Next.js, Node, \& React to help facilitate the needs of the class as well as one static knowledge base using markdown \& HUGO featuring supplemental technical learning material.
    \end{zitemize}

%%%%%%% ------------------------------------------------------------------------------- %%%%%%%

\subsection*{Automation Developer {\normalsize \normalfont(Contract) } \hfill  May 2022 --- Dec 2022 }
\subtext{Begin Software \hfill Remote }  
    \begin{zitemize}
        \item Integrated multiple APIs \& webhooks from our clients' choice SAAS services, applications, \& databases in over 20 custom developed data centric automations to improve internal business workflows, customer experience, or prospect acquisition.
        \item Developed an automation for a client that saves their CEO over 2 hours per day \& converts more paying business customers by storing \& tracking contact details/sales progress to timely send call to action emails at different pipeline stages.
    \end{zitemize}

%%%%%%% ------------------------------------------------------------------------------- %%%%%%%

\subsection*{Software Engineer {\normalsize \normalfont} \hfill  Feb 2022 --- Aug 2022 }
\subtext{Inkfluencer \hfill Remote }  
    \begin{zitemize}
        \item Developed several backend services relating to user public profiles, advertisement listings, Stripe, \& social media integration using Node(TypeScript), Express, PostgreSQL, \& Prisma in accordance with the MVP specifications \& feature set.
        \item Set up client hosting, DNS/domain registration, \& AWS EC2/S3 while assisting with developing the React dashboard \& landing page.
    \end{zitemize}

%%%%%%% ------------------------------------------------------------------------------- %%%%%%%

\subsection*{React Developer \& Community Manager {\normalsize \normalfont(Contract) } \hfill  Aug 2021 --- Mar 2022 }
\subtext{MappyCoin \hfill Remote } 
    \begin{zitemize}
        \item Developed several pages \& components in React from design mockups into a responsive website 1 month ahead of schedule.
        \item Promoted to include management of a community with over 3000 members \& assistance with business and product development.
    \end{zitemize}

%%%%%%% ------------------------------------------------------------------------------- %%%%%%%

\subsection*{Fullstack Developer {\normalsize \normalfont(Internship) } \hfill  May 2021 --- Aug 2021 }
\subtext{CodePath \hfill Remote } 
    \begin{zitemize}
        \item Co-developed Kurios, a crypto currency dashboard using React, Node, Express, PostgreSQL, \& Material-UI while practicing Scrum through team meetings, daily stand-ups, code reviews, \& sprint planning with engineers.
        \item Performed 35,000 daily cron-scheduled API calls to retrieve \& store real time price data for six currencies saving \$600/month.
        \item Showcased a ”professional” level of technical discipline \& collaborative communication as measured in an evaluation rubric graded by my supervisor by exceeding intern level expectations \& delivering a robust project.
    \end{zitemize}





%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  EDUCATION
%%%%%%% --------------------------------------------------------------------------------------
\section{Education}
\subsection*{Bachelor's of Science in Computer Science, {\normalsize \normalfont Western Governors University} \hfill Dec 2022 --- May 2024} 
\vspace{0.2cm}
\subsection*{Fullstack Web Development Bootcamp, {\normalsize \normalfont San Jose State University} \hfill May 2021 --- Nov 2021} 
\vspace{0.2cm}
\subsection*{Associate's of Science in Computer Information Systems, {\normalsize \normalfont Mission College} \hfill Aug 2020 --- Dec 2022} 
\vspace{0.2cm}
\subsection*{Associate's of Arts in Liberal Arts: Natural Science and Math, {\normalsize \normalfont Mission College} \hfill Aug 2017 --- May 2020} 
{\hfill}


%%%%%%% ---------------------------- END DOC HERE ---------------------------- %%%%%%% 
\end{document}